Pillar 1 - Sequential Pattern Mining

### 2019-02-18 Pillar 1 - Sequential Pattern Mining.Rmd

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
```

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules <- function(rules){

@@

    filter(
      count >= 10
      ) %>%

    mutate_if(
      is.numeric,
      funs(round(., 5))
    ) %>%

    select(
      lhs       , rhs,
      support   , count,
      confidence, rhs.support,
      lift,
      matches("rhsTake")
    ) %>%

    arrange(
      desc(count)
    )

@@

```{r edit rules}
AR <- lapply(
  X   = AR,
  FUN = edit_rules
  )

SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/rules.RDATA"
  )
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
```

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
filter_rules <- function(rules){

@@

    filter(
      count >= 10
      )

@@

```{r edit rules}
AR <- lapply(
  X   = AR,
  FUN = filter_rules
  )

SR <- lapply(
  X   = SR,
  FUN = filter_rules
  )
```

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )
```
